Tensor anisotropy as a tracer of cosmic voids

### 2015-05-26 cosmic_voids.tex
resuelto issue #18 sobre la seccion 3.3 y el sampleo en grid cartesiana

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the density field
instead of the FA field as we do here
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
However, from the analysis of our results the choice of a fixed
Cartesian mesh does not induce spurious results, at least with
the mass resolution we have in the N-body simulation.

>>>>

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the density field
instead of the FA field as we do here
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
\before{However, from the analysis of our results the choice of a fixed
Cartesian mesh does not induce spurious results, at least with
the mass resolution we have in the N-body simulation. }
\after{Nevertheless, in our case the average number of particles per cell
  is large enough ($512$ particles/cell) ensuring that the lowest
  density regions are sampled with at least $\sim 10$ particles
  ($\delta \sim-0.98$), which seems to avoid spurious results from a
  noisy density field sampling.}
